Carbonate chemistry at Ny-Ålesund: AWIPEV-CO~2~ Project

### 2019-04-29 awipev-CO2.Rmd
seaFET period number 13 readjusted to take in consideration seaFET data corrected from 2019-01-29 to 2019-02-07

#put interval in a list with the start date of seaFET measurements
sfinterv <- c( as_datetime("2017-08-24 13:00:00"), sfPeriod[,4])
 #Change period sfinterv[6]. Because seafet was off and on on the 2018-04-24 19:00:00
sfinterv[6] <- ymd_hms("2018-04-24 18:00:00")

>>>>

#put interval in a list with the start date of seaFET measurements
sfinterv <- c( as_datetime("2017-08-24 13:00:00"), sfPeriod[,4])
 #Change period sfinterv[6]. Because seafet was off and on on the 2018-04-24 19:00:00
sfinterv[6] <- ymd_hms("2018-04-24 18:00:00")
 #Change period sfinterv[6]. Because seafet was off and on on the 2018-04-24 19:00:00
sfinterv[14] <- ymd_hms("2019-01-29 16:00:00")
